Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-10 paper.tex
add privacy subsection

\begin{enumerate}
  \item Dissemination of information through means of piracy and torrenting
    gives access to those within areas where Internet shutdowns are commonplace.

  \item Piracy provides a way around an oppressive regime, which are on the
    rise.~\cite{current:jigsaw}

  \item IP laws arbitrarily restrict free speech / invention just because
    someone came up with it first.~\cite[1339]{lemley:faith-based} They are
    based on the assumption that, in doing so, they are encouraging creativity
    (to be first to invent/create), when, in reality, creativity doesn't always
    come first, but may rather be an improvement upon the established. The most
    creative solution is not always the first one. IP laws and restrictions
    block slight innovations upon the existing intellectual property.
\end{enumerate}

\subsection{Privacy}

\begin{enumerate}
  \item Piracy gives you access to cracked versions of software that provide
    more sensible privacy/freedom than what is accessible
    legally.~\cite{stallman:right-to-read}
\end{enumerate}

>>>>

\subsection{Privacy}
As a side note, there are instances where pirated software can be more privacy-oriented
than the paid version. Sometimes the pirated version is ``cracked'' to remove certain
digital rights management (DRM) tools that often run background tasks unbeknownst to the
user. These background tasks often leak bits of information about the user in order to
validate that they are legitimate owners of the software. By collecting information about
users, a business invades the privacy of its user base. However, pirated and cracked
software does not have such DRM because it needed to be removed to allow it to be freely
distributed. Thus, when it comes to software that contains aggressive DRM, piracy offers
better security by default. Unfortunately, some pirated software introduces malicious
code, a subject that will be explored in the next section.
